I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-18 Paper/Paper_noProof.tex
number for 6x500

		\hline
		\text{DNN}  & DeepPoly & PRIMA &  \multicolumn{2}{@{}c@{}|}{\text{ $\beta$-CROWN (pureBaB)}} & 
		Comp(adapt.) & Upper\\ 
		 & / CROWN & (refined) & TO=30s & TO=1200s & fast & Bound\\
		\hline \hline

@@

		$\epsilon = 0.035$ & 34s & 119s & 18.4s & 576s & 925s &\\ \hline
	\end{tabular}
	\caption{$\%$ of verified images and average runtime in seconds, over 200 images.}
	\label{tab:example3}
	\vspace{-1cm}
\end{table}

>>>>

		\hline
		\text{DNN}  & DeepPoly & PRIMA &  \multicolumn{2}{@{}c@{}|}{\text{ $\beta$-CROWN (pureBaB)}} & 
		Comp(adapt.) & Upper\\ 
		 & / CROWN & (refined) & TO=30s & TO=2000s & fast & Bound\\
		\hline \hline

@@

		$\epsilon = 0.035$ & 34s & 119s & 18.4s & 954s & 925s &\\ \hline
	\end{tabular}
	\caption{$\%$ of verified images and average runtime in seconds, over 200 images.}
	\label{tab:example3}
	\vspace{-1cm}
\end{table}
